\name: A hierarchical Bayesian model for Supernova Cosmology

### 2017-10-03 papers/methods/paper.tex
Updating paper

With the well sampled approximation as specified previously, we can remove the redshift integral in Eq \eqref{eq:w1} and replace it with a correction for each observed supernova. For the error function (DES) and skew normal selection (LowZ) functions respectively, this correction becomes
\begin{align}
w_{\rm DES} &= \Phi^c\left(  \frac{m^*_B - \mu_{\rm DES}}{\sqrt{\sigma^{*2}_{m_B} + \sigma_{\rm DES}^2}}  \right) \\
w_{\rm LowZ} &= \mathcal{N}\left( \frac{m_B^* - \mu_{\rm LowZ}}{\sqrt{\sigma^{*2}_{m_B} + \sigma_{\rm LowZ}^2}}\right) \times \notag\\
&\quad\quad \Phi\left(  \frac{{\rm sign}(\alpha_{\rm LowZ})(m_B^* - \mu_{\rm LowZ})}{\frac{\sigma_{m_B}^{*2} + \sigma^2_{\rm LowZ}}{\sigma^2_{\rm LowZ}} \sqrt{\frac{\sigma^2_{\rm LowZ}}{\alpha^2_{\rm LowZ}} + \frac{\sigma_{m_B}^{*2} \sigma^2_{\rm LowZ}}{\sigma_{m_B}^{*2} + \sigma^2_{\rm LowZ}}} }\right),
\end{align}
where $\Phi$ represents the normal CDF function, and $\Phi^c$ the complimentary CDF.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_simple_test_cosmo.pdf}
	\end{center}
	\caption{Posterior surfaces for 22 realisations of supernova data with the Flat $\Lambda$CDM model.}
	\label{fig:simple_om}
\end{figure}
\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_simple_test_w_cosmo.pdf}
	\end{center}
	\caption{Posterior surfaces for 22 realisations of supernova data with the Flat $w$CDM model.}
	\label{fig:simple_w}
\end{figure}
\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_simple_test_ol_cosmo.pdf}
	\end{center}
	\caption{Posterior surfaces for 22 realisations of supernova data with the $\Lambda$CDM model.}.
	\label{fig:simple_ol}
\end{figure}
\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_simple_test_summary.pdf}
	\end{center}
	\caption{Parameter summaries for 22 realisations of supernova data with the Flat $\Lambda$CDM model.}.
	\label{fig:simple_om_summary}
\end{figure}

@@

Early analyses often treated intrinsic dispersion simply as scatter in the underlying absolute magnitude of the underlying population, but recent analyses require more a more sophisticated approach. In our development of this model and tests of intrinsic dispersion, we analyse the effects of three different scatter models. The first is simplest model - coherent magnitude scatter. The second model is the \citet[][hereafter denoted the {\gten} scatter model]{Guy2010}, which models intrinsic scatter with a 70\% contribution from coherent variation and 30\% from chromatic variation. The third model, denoted the {\celeven} model is sourced from \citet{Chotard2011} and has variation with 25\% contribution from coherent scatter and 75\% from chromatic variation.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_bulk_load_summary.pdf}
	\end{center}
	\caption{Parameter summaries for 20 realisations of supernova data with the Flat $\Lambda$CDM model.}.
	\label{fig:bulk_summary}
\end{figure}

@@

\subsubsection{Spectroscopic Sample}

\subsubsection{Photometric sample}

\subsection{Comparison with bells and whistles fixed}

@@

\section{Interesting Implementation Details}
\label{sec:details}
Anything interesting.

Also talk about non-analytic correction factors (and their failure - mc integration, GP, NNGP)

@@

>>>>

With the well sampled approximation as specified previously, we can remove the redshift integral in Eq \eqref{eq:w1} and replace it with a correction for each observed supernova. For the error function (DES) and skew normal selection (LowZ) functions respectively, this correction becomes
\begin{align}
w_{\rm DES} &= \Phi^c\left(  \frac{m^*_B - \mu_{\rm DES}}{\sqrt{\sigma^{*2}_{m_B} + \sigma_{\rm DES}^2}}  \right) \\
w_{\rm LowZ} &= 2\mathcal{N}\left( \frac{m_B^* - \mu_{\rm LowZ}}{\sqrt{\sigma^{*2}_{m_B} + \sigma_{\rm LowZ}^2}}\right) \times \notag\\
&\quad\quad \Phi\left(  \frac{{\rm sign}(\alpha_{\rm LowZ})(m_B^* - \mu_{\rm LowZ})}{\frac{\sigma_{m_B}^{*2} + \sigma^2_{\rm LowZ}}{\sigma^2_{\rm LowZ}} \sqrt{\frac{\sigma^2_{\rm LowZ}}{\alpha^2_{\rm LowZ}} + \frac{\sigma_{m_B}^{*2} \sigma^2_{\rm LowZ}}{\sigma_{m_B}^{*2} + \sigma^2_{\rm LowZ}}} }\right),
\end{align}
where $\Phi$ represents the normal CDF function, and $\Phi^c$ the complimentary CDF.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_simple_test_cosmo.pdf}
	\end{center}
	\caption{Posterior surfaces for 22 realisations of supernova data with the Flat $\Lambda$CDM model.}
	\label{fig:simple_om}
\end{figure}
\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_simple_test_w_cosmo.pdf}
	\end{center}
	\caption{Posterior surfaces for 22 realisations of supernova data with the Flat $w$CDM model.}
	\label{fig:simple_w}
\end{figure}
\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_simple_test_ol_cosmo.pdf}
	\end{center}
	\caption{Posterior surfaces for 22 realisations of supernova data with the $\Lambda$CDM model.}
	\label{fig:simple_ol}
\end{figure}
\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_simple_test_summary.pdf}
	\end{center}
	\caption{Parameter summaries for 22 realisations of supernova data with the Flat $\Lambda$CDM model.}
	\label{fig:simple_om_summary}
\end{figure}

@@

Early analyses often treated intrinsic dispersion simply as scatter in the underlying absolute magnitude of the underlying population, but recent analyses require more a more sophisticated approach. In our development of this model and tests of intrinsic dispersion, we analyse the effects of three different scatter models. The first is simplest model - coherent magnitude scatter, denoted `Smear' in the figures. The second model is the \citet[][hereafter denoted the {\gten} scatter model]{Guy2010}, which models intrinsic scatter with a 70\% contribution from coherent variation and 30\% from chromatic variation. The third model, denoted the {\celeven} model is sourced from \citet{Chotard2011} and has variation with 25\% contribution from coherent scatter and 75\% from chromatic variation.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{approximate_bulk_load_summary.pdf}
	\end{center}
	\caption{Parameter summaries for 20 realisations of supernova data with the Flat $\Lambda$CDM model. {\red Discuss any biases}}
	\label{fig:bulk_summary}
\end{figure}

{\red More discussion here when I get more results}

@@

{\red Put in multisim forecasts with systamtics both on and off}

@@

@@

Plots of posterior surfaces and parameter summaries were created with \verb|ChainConsumer| \citep{Hinton2016}.
